The prospectus currently has four projects in anticipation that at least one would not be completed and I will quickly move on to the others. I list the tentative time line below with an uncertainty estimate.

\subsection{Two-sided logit model}
\begin{itemize}
\item Obtain the PCI data (\textbf{done})
\item Obtain the Bureau of Economic Analysis' (BEA) database of US FDI (\textbf{contacted Duke librarian and the BEA}). It solely depends on whether the BEA gives graduate student on-site access to the data (high uncertainty). \textbf{January 2016}
\item Implement the EM algorithm for TSL model (high uncertainty, given that I'll code this up myself and complex models always have to possibility of not converging). \textbf{December 2016}
\end{itemize}

\subsection{Diff-in-Diff using OECD Anti-bribery convention}

\begin{itemize}
\item Obtain PCI data before and after the OECD ABC phase 3 enforcement. \textbf{done}
\item Calculate spillover effect using Enterprise Census data (high uncertainty, given that I have not worked extensively with this dataset and that it needs a lot of merging to calculate vertical, i.e. inter-industry, spillover). \textbf{February 2016}
\item Analyze the data (low uncertainty, given the diff-in-diff design). Finish the chapter. \textbf{April 2016}
\end{itemize}

\subsection{Survey experiment in Vietnam}

Given the nature of elite surveys, this project has the most uncertainties overall.

\begin{itemize}
\item Contact local researchers to gauge the project's feasibility. \textbf{February 2016}
\item Travel to Vietnam to interview officials and implement the survey. \textbf{May -- August 2016}
\item Analyze (low uncertainty, given the experimental design and available R package for conjoint analysis). Finish the chapter. \textbf{October 2016}
\end{itemize}

\subsection{Instrumental variable}
\begin{itemize}
\item Obtain World Bank Enterprise Survey data. \text{done}
\item Obtain the BEA's data on FDI into the US. \text{contacted Duke librarian and the BEA}. This project depends on whether the BEA gives me on-site access to the confidential, firm-level data (high uncertainty). \textbf{January 2016}
\item Create the instrumental variable by measuring spillover effect by sector for FDI in the US. \textbf{February 2017}
\item Analyze and finish the chapter. \textbf{April 2017}
\end{itemize}